### 2016-07-08 paper/icse2017/modes.tex
adjusting tables

Modern build systems provides a means to reveal test flakiness.  The
typical approach is to iteratively execute the test suite multiple
times and to mark tests that produce both pass and failing outputs.
More precisely, the developer determines a bound N for the number of
re-executions of the test suite.  Only tests that fail in one given
iteration (consequently, failed in all previous iterations) are
scheduled for re-execution in the next iteration.  At the end of the
process, a test is considered passing if it passes in the first
iteration, a test is considered failing if it fails in all iterations,
and it is considered flaky if it fails in all iterations but the last
it executed.  The process terminates when all tests eventually pass or
when bound N is reached.  Note that every iteration runs a subset of
the test from the previous iteration so execution cost is lower
compared to executing the suite N times.  To note that ITE is
supported by the popular maven surefire
plugin~\cite{maven-surefire-plugin}.\Fix{mention which
  flag/parameter...} ITE provides a means to acknowledge the presence
of test flakiness, including \pef{}s.  Ideally, one would like to
eliminate \pef{}s and avoid the need for ITE.

>>>>

Modern build systems provide a means to reveal test flakiness.  The
typical approach is to execute the test suite multiple times and
iteratively mark as flaky those tests that produce both pass and
failing outputs.  More precisely, the process starts with the
developer determining a bound N for the number of re-executions of the
test suite.  Only tests that fail in one given iteration
(consequently, failed in all previous iterations) are scheduled for
re-execution in the next iteration.  At the end of the process, a test
is considered passing if it passes in the first iteration, a test is
considered failing if it fails in all iterations, and it is considered
flaky if it fails in all iterations but the last it executed.  The
process terminates when all tests eventually pass or when the bound N
is reached.  Note that every iteration runs a subset of the test from
the previous iteration so execution cost is lower compared to
executing the entire test suite N times.  To note that this iterative
process is supported by the popular maven surefire
plugin~\cite{maven-surefire-plugin}.\Fix{others?  mention which
  flag/parameter...}  Ideally, one would like to eliminate \pef{}s and
avoid the need for re-executing the test suite multiple times.
